---
title: "Errata"
subtitle: "On Coppock, Green and Porter (2022), *Research & Politics* 9(1)"
format:
  pdf:
    output-file: coppock_green_porter_2022_errata.pdf
    geometry: margin=1.25in
    fontsize: 11pt
    include-in-header:
      text: |
        \usepackage{caption}
        \captionsetup{labelformat=empty}
        \usepackage{float}
        \floatplacement{table}{H}
        \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(here)
library(tidyverse)
here::i_am("errata.qmd")

t4 <- read_csv(here("maintained", "output", "table_4_vote_share_precinct.csv"),
               show_col_types = FALSE) |>
  filter(model == "Model 1", term == "Z")
b3 <- read_csv(here("maintained", "output", "table_b3_vote_share_precinct_cd.csv"),
               show_col_types = FALSE) |>
  filter(term == "Z")
fg2 <- read_csv(here("maintained", "output", "figure_g2_design_diagnosis.csv"),
                show_col_types = FALSE)
```

This note lists four errors in "Does digital advertising affect vote choice? Evidence from a randomized field experiment," published in *Research & Politics* 9(1), doi [10.1177/20531680221076901](https://doi.org/10.1177/20531680221076901). **None of them changes a conclusion of the paper.** They are recorded because the numbers themselves are wrong and a reader who quoted them would be misled.

Item 1 is a misstated number in the text. Items 2 through 4 are errors in the appendix: two of labelling, one of a table printed in place of another. Every corrected value below is computed from the deposited replication archive ([10.7910/DVN/UH2NQW](https://doi.org/10.7910/DVN/UH2NQW)) at the time this document is rendered. The maintained code is at [github.com/active-maintenance-aec/coppock_green_porter_2022](https://github.com/active-maintenance-aec/coppock_green_porter_2022).

## 1. The unadjusted estimate is misstated by a factor of ten

Published, p. 5:

> ...a **2.1 percentage point** increase in Democratic vote share, though this estimate is uncertain, as evidenced by its large **standard error of 3.0 percentage points**.

Corrected:

> ...a **`r sprintf("%.1f", t4$estimate*100)` percentage point** increase in Democratic vote share, though this estimate is uncertain, as evidenced by its large **standard error of `r sprintf("%.1f", t4$std.error*100)` percentage points**.

Table 4 reports `r sprintf("%.4f", t4$estimate)` with a standard error of `r sprintf("%.4f", t4$std.error)`, which is `r sprintf("%.2f", t4$estimate*100)` and `r sprintf("%.2f", t4$std.error*100)` percentage points; the corrected sentence carries them at the one decimal the published sentence uses. The next sentence in the article applies percentage point units correctly to the adjusted estimate. The published standard error of 3.0 corresponds to no model in the paper or the appendix. The claim the sentence makes is unaffected: on either reading the unadjusted estimate is small and swamped by its standard error, and the paper's conclusion rests on the covariate-adjusted estimate in column 2, which is reported and interpreted correctly throughout.

## 2. Figure G.2 names the wrong effect size

Published, panel annotation:

> Power when PATE = **0.1**

Corrected:

> Power when PATE = **`r fg2$pate_center`**

The simulated effects are drawn from a normal distribution centred at `r fg2$pate_center`, which is what the appendix text says two paragraphs earlier. The label is a hardcoded string in the analysis script; nothing plotted is affected. The corrected figure:

```{r fig-g2}
#| out-width: 100%
#| fig-align: center
#| fig-cap: "Figure G.2 (corrected)"
knitr::include_graphics("maintained/output/figure_g2_design_diagnosis.pdf")
```

\parbox{\linewidth}{\footnotesize\raggedright \textit{Note:} Figure G.2 as published, with the panel annotation corrected. Nothing plotted differs. Drawn from the deposited replication archive by \texttt{maintained/figure\_g2\_design\_diagnosis.R}.}

## 3. Covariate row labels are wrong in five appendix tables

Thirteen covariate rows across Tables E.7, F.8, F.9, F.10 and F.11 name a variable the model does not contain. No coefficient, standard error or summary statistic is affected; the estimates beside the wrong labels are the ones the caption describes.

Published, Tables E.7 and F.8, each of the three lagged covariate rows:

> **Two Party Vote Share**

Corrected:

> **Two Party Vote Margin**

Both balance models regress the treatment indicator on lagged two-party vote *margins*, not shares.

Published, Tables F.9, F.10 and F.11, the first covariate row:

> **Missingness Indicator (2016)**

Corrected, respectively:

> **Two Party Vote Share (2016)**, **Two Party Vote Margin (2016)**, **Two Party Vote Total (2016)**

No ZIP code is missing 2016 returns, so the ZIP-level models carry no 2016 missingness indicator, and the label vector in the analysis script names one anyway. The same vector is reused for all three outcomes, which is also why the 2014 and 2012 covariate rows of Tables F.10 and F.11 read **Two Party Vote Share** where the regressors are vote margins and vote totals. The 2014 and 2012 rows of Table F.9 are correct as published.

All five tables are reprinted below with corrected labels and otherwise unchanged.

\begingroup
\input{maintained/output/table_e7_balance_precinct.tex}
\input{maintained/output/table_f8_balance_zip.tex}
\input{maintained/output/table_f9_vote_share_zip.tex}
\input{maintained/output/table_f10_vote_margin_zip.tex}
\input{maintained/output/table_f11_turnout_zip.tex}
\endgroup

\parbox{\linewidth}{\footnotesize\raggedright \textit{Note:} Tables E.7, F.8, F.9, F.10 and F.11 as published, with covariate row labels corrected. Every coefficient, standard error and summary statistic is unchanged. Estimated from the deposited replication archive by the correspondingly named scripts under \texttt{maintained/}.}

## 4. Appendix Table B.3 reprints Table B.4

Table B.3 is captioned "Effects on vote share (CD fixed effects)." Every cell beneath that caption is identical to Table B.4, "Effects on vote margin (CD fixed effects)": the same coefficients, standard errors, R-squared values and covariate labels, all on the vote margin scale. The vote share models with congressional district fixed effects appear nowhere in the appendix.

Those models are estimable from the deposited data. The effect of any treatment video on vote share with district fixed effects is `r sprintf("%.4f", b3$estimate[1])` (`r sprintf("%.4f", b3$std.error[1])`) without covariates, the same substantive result as Table 4. The table that should have appeared:

\begingroup
\input{maintained/output/table_b3_vote_share_precinct_cd.tex}
\endgroup

\parbox{\linewidth}{\footnotesize\raggedright \textit{Note:} Estimated from the deposited replication archive by \texttt{maintained/table\_b3\_vote\_share\_precinct\_cd.R}, which fits the vote share models with congressional district fixed effects that Table B.3 was captioned for. Standard errors in parentheses; $*$ denotes $p < 0.05$.}
